Probabilistic Catalogs from Crowded Star Fields

### 2012-07-27 paper/ms.tex
Tidying up Pareto calc
Results for normalisation of broken Pareto
Acknowledgements
Deriving by complementary CDF instead - much cleaner

@@

\section{Broken Pareto Distribution}
The Broken Pareto distribution is:
\begin{eqnarray}
p(x | \theta) &\propto&
\left\{
\begin{array}{lcr}
0, & & x < x_0 \\
x^{-\alpha_1 - 1}, & & x_0 \leq x \leq x_1 \\
x^{-\alpha_2 - 1}, & & x > x_1
\end{array}
\right.
\end{eqnarray}
We will need the fully normalised version. Putting in two normalising constants:
\begin{eqnarray}
p(x | \theta) &=&
\left\{
\begin{array}{lcr}
0, & & x < x_0 \\
C_1x^{-\alpha_1 - 1}, & & x_0 \leq x \leq x_1 \\
C_2x^{-\alpha_2 - 1}, & & x > x_1
\end{array}
\right.
\end{eqnarray}
The normalising constants can be obtained by enforcing the following
constraints. The first constraint is that the total probability is unity:
\begin{eqnarray}
\int p(x|\theta) \, dx = 1
\end{eqnarray}
The second constraint is that the PDF should be continuous at $x=x_1$:
\begin{eqnarray}
C_1 x_1^{-\alpha_1 - 1} = C_2 x_1^{-\alpha_2 - 1}
\end{eqnarray}

>>>>

\section{Acknowledgements}
BJB would like to thank his teaching mentor Dr Wayne Stewart.
Marshall, Lang, ...

@@

\section{Broken Pareto Distribution}

Consider the complementary CDF:
\begin{eqnarray}
G(x) = P(X \geq x)
\end{eqnarray}
The complementary CDF for a broken Pareto is:
\begin{eqnarray}
G(x) &=&
\left\{
\begin{array}{lcr}
1, & & x < x_1 \\
\left(\frac{x_1}{x}\right)^{-\alpha_1}, & & x_1 \leq x \leq x_2 \\
K\left(\frac{x_2}{x}\right)^{-\alpha_2}, & & x > x_2
\end{array}
\right.
\end{eqnarray}

%The Broken Pareto distribution is:
%\begin{eqnarray}
%p(x | \theta) &\propto&
%\left\{
%\begin{array}{lcr}
%0, & & x < x_0 \\
%x^{-\alpha_1 - 1}, & & x_0 \leq x \leq x_1 \\
%x^{-\alpha_2 - 1}, & & x > x_1
%\end{array}
%\right.
%\end{eqnarray}
%where the parameters are $\theta = \{x_0, x_1, \alpha_0, \alpha_1\}$.
%We will need the fully normalised version. Putting in two normalisers:
%\begin{eqnarray}
%p(x | \theta) &=&
%\left\{
%\begin{array}{lcr}
%0, & & x < x_0 \\
%Z_1^{-1}x^{-\alpha_1 - 1}, & & x_0 \leq x \leq x_1 \\
%Z_2^{-1}x^{-\alpha_2 - 1}, & & x > x_1
%\end{array}
%\right.
%\end{eqnarray}
%The normalising constants can be obtained by enforcing the following
%constraints. The first constraint is that the PDF should be continuous at
%$x=x_1$:
%\begin{eqnarray}
%Z_1^{-1} x_1^{-\alpha_1 - 1} &=& Z_2^{-1} x_1^{-\alpha_2 - 1} \\
%\implies Z_2 &=& x_1^{\alpha_1-\alpha_2}Z_1 \label{constraint1}
%\end{eqnarray}
%The second constraint is that the total probability is unity:
%\begin{eqnarray}
%\int p(x|\theta) \, dx &=& 1 \\
%\implies
%\int_{x_0}^{x_1} Z_1^{-1}x^{-\alpha_1 - 1} \, dx
%+ \int_{x_1}^{\infty} Z_2^{-1}x^{-\alpha_2 - 1} \, dx &=& 1 \label{constraint2}
%\end{eqnarray}
%Combining equations~\ref{constraint1} and~\ref{constraint2} yields:
%\begin{eqnarray}
%Z_1 &=& \frac{x_0^{-\alpha_1} - x_1^{-\alpha_1}}{\alpha_1} + \frac{x_1^{-\alpha_1}}{\alpha_2}\\
%Z_2 &=& x_1^{\alpha_1-\alpha_2}Z_1
%\end{eqnarray}

%The cumulative distribution can be obtained:
%\begin{eqnarray}
%F(x) &=& \int_{x_0}^x p(x|\theta) \, dx \\
%&=&
%\left\{
%\begin{array}{lcr}
%0, & & x < x_0 \\
%\frac{x_0^{-\alpha_1} - x^{-\alpha_1}}{Z_1\alpha_1}, & & x_0 \leq x \leq x_1 \\
%, & & x > x_1
%\end{array}
%\right.
%\end{eqnarray}
